CS6213 Project Report

### 2021-05-07 report/paper.tex
WIP

>>>>

We spent a not insignificant amount of time adding further constraints in an attempt to prune
the state space to let TLC find a trace that violates \texttt{CommitWhenConcurrentLeaders} (the property is a negation), and we also experimented with TLC's depth-first search and simulation modes, but to no avail.
%
The state space was just too large.

However, we realised that in fact we are \emph{not} interested in exploring the state space. 
%
Since we are not doing model-checking, but rather counterexample finding, we can be very selective in terms of the states we explore.

Concretely, looking at our property, we see that it is somehow composed of distinct parts:
%
first, there is a trace prefix that leads to two leaders existing at the same time (in different terms; this is allowed in Raft),
%
then, some entry commits,
%
then afterwards, some more steps are taken, and there are still two leaders.
